Hypertension and microbiome

### 2019-01-01 rrbiome.Rmd
Create rds

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, echo = TRUE, message = FALSE, results='asis', cache=TRUE, warning=FALSE)
knitr::opts_chunk$set(cache.path = 'cache/', output.dir="cache/",
                      file.path = 'cache/', fig.path = 'cache/')
```

@@

```{r adonis3, eval = FALSE}
 adonis.species <- calculateadonis(dset = meta(pseq.species),
                    matrix = bray.dist.m.species,
                    covariates = "BL_AGE + SEX",
                    npermutations = 2)

 adonis.species

ret <- list(model_1 = adonis.species$model_1 %>% tibble::rownames_to_column(var = "response"),
     model_2 =  adonis.species$model_2 %>% tibble::rownames_to_column(var = "response"))

data.table::rbindlist(ret, id = "model_name") %>%
    dplyr::filter(response %in% list(a = "MAP", b = "SYSTM"))

    })
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, echo = TRUE, message = FALSE, results='asis', cache=TRUE, warning=FALSE)
knitr::opts_chunk$set(cache.path = 'cache/', output.dir="cache/",
                      file.path = 'cache/', fig.path = 'cache/')

dir.create("rds/", showWarnings = FALSE)
```

@@

```{r adonis3, eval = FALSE}
 adonis.species %>%
    select(response, SumsOfSqs, MeanSqs, F.Model, R2, "Pr(>F)") %>%
    kable(.)
```
